\documentclass[english,man]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

% Table formatting
\usepackage{longtable,booktabs}
\usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable
\usepackage{longtable}              % Allows tables to break across pages

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Perception of Mixed Emotion Across Cultures},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines

\setcounter{secnumdepth}{0}
\ifxetex
  \usepackage{polyglossia}
  \setmainlanguage{}
\else
  \usepackage[english]{babel}
\fi

% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}

 % Line numbering
  \usepackage{lineno}
  \linenumbers


\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{Perception of Mixed Emotion Across Cultures}

  \shorttitle{EMOTION AND CULTURE}


  \author{
          Yay-hyung cho\textsuperscript{1}  }

  \def\affdep{{""}}%
  \def\affcity{{""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} The University of Michigan  }


%   \def\affinst{{"init", "The University of Michigan"}}%
%   \def\affstate{{"init", ""}}%
%   \def\affcntry{{"init", ""}}%

  \note{
    \vspace{1cm}
    Author note

    \raggedright
    \setlength{\parindent}{0.4in}

    \newcounter{author}

%     %     %       %       \setcounter{author}{0}
%         %           \addtocounter{author}{1}
%         %         \expandafter\edef\csname authorid\endcsname{\theauthor}
%         Yay-hyung cho, \pgfmathparse{\affdep[\authorid]} \pgfmathresult, \pgfmathparse{\affinst[\authorid]} \pgfmathresult, \pgfmathparse{\affcity[\authorid]} \pgfmathresult, \pgfmathparse{\affstate[\authorid]} \pgfmathresult, \pgfmathparse{\affcntry[\authorid]} \pgfmathresult
%       %     .
%     
    Complete departmental affiliations for each author (note the
    indentation, if you start a new paragraph).
    
    Enter author note here.

                      Correspondence concerning this article should be addressed to Yay-hyung cho, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
                }

  \abstract{Enter abstract here (note the indentation, if you start a new
paragraph).}
  \keywords{keywords \\

    \indent Word count: X
  }


\begin{document}

\maketitle



{[}1{]} 5.440247e-10 df 111.2358 mean in group american mean in group
japanese 0.367284 1.641304

\section{Test}\label{test}

(M=1.64,p=0.00)

\section{Methods}\label{methods}

We report how we determined our sample size, all data exclusions (if
any), all manipulations, and all measures in the study.

\subsection{Sample}\label{sample}

\subsection{Material}\label{material}

\subsection{Procedure}\label{procedure}

\subsection{Data analysis}\label{data-analysis}

We used R (3.3.0, R Core Team, 2015b) and the R-packages \emph{papaja}
(0.1.0.9054, Aust \& Barth, 2015), and \emph{foreign} (0.8.66, R Core
Team, 2015a) for all our analyses.

\section{Results}\label{results}

\section{Discussion}\label{discussion}

\section{References}\label{references}

\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
\setlength{\parskip}{8pt}

Aust, F., \& Barth, M. (2015). \emph{Papaja: Create aPA manuscripts with
rMarkdown}. Retrieved from \url{https://github.com/crsh/papaja}

R Core Team. (2015a). \emph{Foreign: Read data stored by minitab, s,
sAS, sPSS, stata, systat, weka, dBase, .} Retrieved from
\url{https://CRAN.R-project.org/package=foreign}

R Core Team. (2015b). \emph{R: A language and environment for
statistical computing}. Vienna, Austria: R Foundation for Statistical
Computing. Retrieved from \url{https://www.R-project.org/}



\end{document}
